Learning to Group and Order AMR Semantics for General Purpose Discourse Planning

### 2015-12-10 paper/paper.tex
rename some tables for consistency
change all data to two decimals

\begin{table}[H]
\centering
\caption{Features used by subgraph partition scorer}
\label{tab:subgraph_selection_features}
\begin{tabular}{@{}ll@{}}
\toprule
\textbf{Feature}                      & \textbf{Weight} \\ \midrule
\# groups in partition                & 10.29970016     \\
\# groups in partition squared        & -1.17590317     \\
mean \# facts per partition           & 1.09239105      \\
max \# facts per partition            & -0.21350766     \\
min \# facts per partition            & 0.11910551      \\
std\_dev \# facts per partition       & 0.20101274      \\
mean pairwise subgraph similarity     & -18.66465415    \\
min pairwise subgraph similarity      & 1.77360275      \\
max pairwise subgraph similarity      & -0.38517871     \\
std\_dev pairwise subgraph similarity & -7.56089457     \\
mean pairwise verb set similarity     & -1.02945557     \\
min pairwise verb set similarity      & 0.04030027      \\
max pairwise verb set similarity      & 0.89961397      \\
std\_dev pairwise verb set similarity & -0.17388411     \\ \bottomrule
\end{tabular}
\end{table}

@@

\begin{table}
\centering
\label{tab:order_features}
\begin{tabular}{|r|c|c|}
\hline
Feature & \\ \hline\hline
Pairwise Jaccard & Jaccard similarity of the AMR graphs for sentences $s_i,s_{i+1}$ \\ \hline
Two-apart Jaccard & Jaccard similarity of the AMR graphs for sentences $s_i,s_{i+2}$ \\ \hline
Pairwise node Jaccard & Jaccard similarity of just the vertex sets for sentences $s_i,s_{i+1}$ \\ \hline
Combined Jaccard & Jaccard similarity between the paragraph AMR and $s_i \cup
s_{i+1}$ \\ \hline
\end{tabular}
\caption{Subgraph Ordering Features}
\end{table}

\begin{table}
\centering
\begin{tabular}{|r|c|c|}
\hline
Feature & Weight \\ \hline\hline
mean pairwise Jaccard & -5.00181089 \\ \hline
std\_dev pairwise Jaccard & -0.33312514 \\ \hline
min pairwise Jaccard & 2.60603159 \\ \hline
max pairwise Jaccard & 1.55569119 \\ \hline
mean two-apart Jaccard & 4.19364855 \\ \hline
std\_dev two-apart Jaccard & 7.77286275 \\ \hline
min two-apart Jaccard & 2.94073393 \\ \hline
max two-apart Jaccard & -4.35272278 \\ \hline
mean pairwise node Jaccard & -0.94370112 \\ \hline
std\_dev pairwise node Jaccard & 4.49617236 \\ \hline
min pairwise node Jaccard & 1.14357291 \\ \hline
max pairwise node Jaccard & -1.94888156 \\ \hline
mean combined Jaccard & 0.47908235 \\ \hline
std\_dev combined Jaccard & -1.84644112 \\ \hline
min combined Jaccard & -0.57636185 \\ \hline
max combined Jaccard & 0.82229913 \\ \hline
\end{tabular}
\caption{Feature weights for Subrgaph Order Scorer}
\end{table}

@@

\begin{table}
\centering
\begin{tabular}{|r|c|c|c|c|c|}
\hline
Approach & Mean  & Std.  & Min & Max \\ \hline\hline
Baseline & 5.009 & 2.091 & 0   & 10  \\ \hline
Greedy   & 1.360 & 0.910 & 0   & 5   \\ \hline
\end{tabular}
\label{tab:order_eval}
\caption{Evaluation results for Subgraph Ordering}
\end{table}

@@

\begin{table}[H]
\centering
\caption{Revised Kendall Tau Results}
\label{tab:experiments}
\begin{tabular}{@{}lllll@{}}
\toprule
\textbf{(Selection, Ordering)} & \textbf{Mean} & \textbf{Std. Dev.} & \textbf{Min} & \textbf{Max} \\ \midrule
Baseline, Baseline & 40.97 & 62.38 & 0 & 634 \\
Greedy, Greedy & 36.43 & 61.22 & 2 & 563 \\
Greedy, Annealing & 34.48 & 50.60 & 2 & 411 \\ \bottomrule
\end{tabular}
\end{table}

@@

\begin{table}[H]
\centering
\caption{Mean number of sentences and facts per sentence for the pipeline}
\label{tab:metrics}
\begin{tabular}{@{}lll@{}}
\toprule
\textbf{(Selection, Ordering)} & \textbf{Mean \# Sentences} & \textbf{Mean \# Facts per Sentence} \\ \midrule
Baseline, Baseline & 6.11 & 2.33 \\
Greedy, Greedy & 5.81 & 2.45\\
Greedy, Annealing & 5.81 & 2.45 \\ \bottomrule
\end{tabular}
\end{table}

@@

\pagebreak
\bibliographystyle{acm}
\bibliography{paper}
\end{document}

>>>>

\begin{table}[H]
\centering
\caption{Features used by subgraph partition scorer}
\label{tab:subgraph_selection_features}
\begin{tabular}{@{}ll@{}}
\toprule
\textbf{Feature}                      & \textbf{Weight} \\ \midrule
\# groups in partition                & 10.30     \\
\# groups in partition squared        & -1.18     \\
mean \# facts per partition           & 1.09      \\
max \# facts per partition            & -0.21     \\
min \# facts per partition            & 0.12      \\
std\_dev \# facts per partition       & 0.20      \\
mean pairwise subgraph similarity     & -18.66    \\
min pairwise subgraph similarity      & 1.77      \\
max pairwise subgraph similarity      & -0.39     \\
std\_dev pairwise subgraph similarity & -7.56     \\
mean pairwise verb set similarity     & -1.03     \\
min pairwise verb set similarity      & 0.04      \\
max pairwise verb set similarity      & 0.90      \\
std\_dev pairwise verb set similarity & -0.17     \\ \bottomrule
\end{tabular}
\end{table}

@@

\begin{table}
\centering
\label{tab:order_features}
\begin{tabular}{|r|c|c|}
\hline
Feature & \\ \hline\hline
Pairwise Jaccard & Jaccard similarity of the AMR graphs for sentences $s_i,s_{i+1}$ \\ \hline
Two-apart Jaccard & Jaccard similarity of the AMR graphs for sentences $s_i,s_{i+2}$ \\ \hline
Pairwise node Jaccard & Jaccard similarity of just the vertex sets for sentences $s_i,s_{i+1}$ \\ \hline
Combined Jaccard & Jaccard similarity between the paragraph AMR and $s_i \cup
s_{i+1}$ \\ \hline
\end{tabular}
\caption{Description of features used by Subgraph Ordering Classifier}
\end{table}

\begin{table}
\centering
\begin{tabular}{|r|c|c|}
\hline
Feature & Weight \\ \hline\hline
mean pairwise Jaccard & -5.00 \\ \hline
std\_dev pairwise Jaccard & -0.33 \\ \hline
min pairwise Jaccard & 2.61 \\ \hline
max pairwise Jaccard & 1.56 \\ \hline
mean two-apart Jaccard & 4.19 \\ \hline
std\_dev two-apart Jaccard & 7.77 \\ \hline
min two-apart Jaccard & 2.94 \\ \hline
max two-apart Jaccard & -4.35 \\ \hline
mean pairwise node Jaccard & -0.94 \\ \hline
std\_dev pairwise node Jaccard & 4.50 \\ \hline
min pairwise node Jaccard & 1.14 \\ \hline
max pairwise node Jaccard & -1.95 \\ \hline
mean combined Jaccard & 0.48 \\ \hline
std\_dev combined Jaccard & -1.85 \\ \hline
min combined Jaccard & -0.58 \\ \hline
max combined Jaccard & 0.82 \\ \hline
\end{tabular}
\caption{Features used by Subgraph Ordering Classifier}
\end{table}

@@

\begin{table}
\centering
\begin{tabular}{|r|c|c|c|c|c|}
\hline
Approach & Mean  & Std.  & Min & Max \\ \hline\hline
Baseline & 5.01 & 2.09 & 0   & 10  \\ \hline
Greedy   & 1.36 & 0.91 & 0   & 5   \\ \hline
\end{tabular}
\label{tab:order_eval}
\caption{Evaluation Metrics for Subgraph Ordering}
\end{table}

@@

\begin{table}[H]
\centering
\caption{Revised Kendall Tau Metrics}
\label{tab:experiments}
\begin{tabular}{@{}lllll@{}}
\toprule
\textbf{(Selection, Ordering)} & \textbf{Mean} & \textbf{Std. Dev.} & \textbf{Min} & \textbf{Max} \\ \midrule
Baseline, Baseline & 40.97 & 62.38 & 0 & 634 \\
Greedy, Greedy & 36.43 & 61.22 & 2 & 563 \\
Greedy, Annealing & 34.48 & 50.60 & 2 & 411 \\ \bottomrule
\end{tabular}
\end{table}

@@

\begin{table}[H]
\centering
\caption{Sentence Metrics for the full pipeline}
\label{tab:metrics}
\begin{tabular}{@{}lll@{}}
\toprule
\textbf{(Selection, Ordering)} & \textbf{Mean \# Sentences} & \textbf{Mean \# Facts per Sentence} \\ \midrule
Baseline, Baseline & 6.11 & 2.33 \\
Greedy, Greedy & 5.81 & 2.45\\
Greedy, Annealing & 5.81 & 2.45 \\ \bottomrule
\end{tabular}
\end{table}

@@

\pagebreak
\bibliographystyle{ieeetr}
\bibliography{paper}
\end{document}
